
# (PART\*) Scientific Literature {-}

<!-- Set up code of OTTR Book-->

```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

## Pre-lab

## Lecture: Reading a paper

*Estimated time: *

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1nGKvSYGHJu0JZLMWZiFu_iGLIC16IKlnWsVyNyjdyek/edit#slide=id.g35f391192_00")

```

[Lecture](https://docs.google.com/presentation/d/1uuuAbg_rcfCVohaVrrxfUfszwTDqigzg34qEWfTNeR0/edit#slide=id.g35f391192_00)


## Activity: Scientific Literature

### Purpose

### Introduction

### Instructions

### Activity 1 - Overview of the paper

*Estimated time: 30 minutes*

Determine the main objectives and purpose of the paper. 

|1. What is the purpose of this study?  |
|:--|
| <br> |
<br>

|2. What is the hypothesis in this study?  |
|:--|
| <br> |
<br>

|3. Describe the knowledge gap. In essence, what did the scientific community not know that this study was trying to answer?|
|:--|
| <br> |
<br>

|4. What were the main conclusions the authors made in this study?|
|:--|
| <br> |
<br>

### Activity 2 - Methods and Figure Analysis (in class and homework)

*Estimated time: 45 minutes*

#### Activity 2.1 – Examine the Methods and Data presented in this study

|1. Summarize one aspect of sample-associated metadata used for this study? e.g. What is the range of subjects’ age; what is the spectrum of subjects’ medical problems?|
|:--|
| <br> |
<br>

|2. Discuss one method or analysis used in this paper.|
|:--|
| <br> |
<br>

|Summarize one figure presented in this paper.|
|:--|
| <br> |
<br>

#### Activity 2.2 - Figures and a Table


Describe the method/approach used to generate this data

|                  |Method/Approach|
|:-----------------|----:|
|Table 1          || 
|Fig. 2     ||
|Fig. 3A       | | 
|Fig. 3B   | |
<br>

Describe main result/observation 

|                  |Main result/Observation|
|:-------|----:|
|Table 1          || 
|Fig. 2     ||
|Fig. 3A       | | 
|Fig. 3B   | |
<br>

#### Activity 3 Conclusions

*Estimated time: 10 min* 

Compare your conclusions to author conclusions. 
- How similar are the conclusions you came up with to the authors? 
- Were there any differences in interpreting the data? 
- Do you think they are over-stating their findings? Do you think their conclusions are accurate and appropriate?

#### Activity 4 Future Directions

*Estimated time: 10 min* 

1. Scientific work builds on previous studies. What do you believe could be the next step to further the work these researchers did?
- What follow-up question(s) do you have for the authors?


2. What is the impact of this research area in general (or this study in particular?)
- Do you believe further research in this area may benefit society? Can we build on what this study found?


### Grading criteria

- Download this assignment as Microsoft Word (.docx) and upload on your LMS (ex. Canvas, Blackboard, Google Classroom)

### Footnotes

#### Resources

[Google Doc](https://docs.google.com/document/d/1Mg9DGVk0EsSfYwl8VsRHb-_QdtZqiBmhWvbhUWkQERc/edit?usp=sharing)
[Paper](https://drive.google.com/file/d/1_0Q8Wqvj2AGLAvhkfwaRB_5sYKLSr0Tx/view?usp=sharing)

#### Contributions and affiliations

- Valeriya Gaysinskaya, Johns Hopkins University
- Frederick Tan, Johns Hopkins University
- Sayumi York, Notre Dame of Maryland University



